---
title: "Kenneth Blake Vernon"
format:
  html:
    mainfont: sans-serif
    fontcolor: "#151314"
    linkcolor: "#BF211E"
    smooth-scroll: true
    page-layout: full
    css: style.css
    embed-resources: true
execute: 
  echo: false
  error: false
  warning: false
  output: asis
editor: source
params:
  appointments: true
  education: true
  publications: true
  presentations: true 
  funding: true
  teaching: true
  affiliations: true
  synergy: true
  committees: false
  students: false
  development: false
  fieldwork: false
---

```{r}
#| include: false

box::use(
  dplyr[...],
  googlesheets4[read_sheet],
  here[here],
  htmltools[div, HTML],
  kableExtra[kbl, kable_styling],
  knitr[...],
  purrr[map],
  RefManageR[...],
  stringr[str_glue],
  tidyr[...],
  ./helpers[bibliography, format_entries, make_blocks]
)

options(knitr.kable.NA = "")

here("_credentials.RData") |> load()

bib <- bibliography(
  collection, 
  zotero, 
  selection = c("Article", "Review", "Report", "Manuscript", "Presentation")
)

```

::::::::: {#profile}
::: {#address}
Center for Collaborative Synthesis in Archaeology  
Institute of Behavioral Science  
University of Colorado, Boulder  
1440 15th Street  
Boulder, CO 80302  
(303) 492-8147  
:::

::: {#social}
[kbvernon.io](https://www.kbvernon.io/) {{< iconify fa6-solid:image-portrait >}}  
[kbvernon](https://github.com/kbvernon) {{< iconify fa:github >}}  
[0000-0003-0098-5092](https://orcid.org/0000-0003-0098-5092) {{< iconify academicons:orcid >}}  
[2PE4za4AAAAJ](https://scholar.google.com/citations?user=2PE4za4AAAAJ&hl=en) {{< iconify academicons:google-scholar >}}  
:::
:::::::::

::: {#disclaimer}
CV last updated on `r Sys.Date()`
:::

::::::::: {#main}
:::::: {.content-visible when-meta="params.appointments"}

## {{< iconify fa-solid:briefcase >}} Appointments

```{r}

read_sheet(google_page_id, sheet = "appointments")  |>
  mutate(
    end = ifelse(is.na(end), "present", end),
    x = str_glue("<strong>{title}</strong><br>{organization}"),
    y = str_glue("{start}-{end}")
  ) |> 
  arrange(desc(start)) |> 
  select(x, y) |> 
  kbl(
    escape = FALSE,
    col.names = NULL,
    align = c('l', 'r')
  ) |>
  kable_styling(full_width = TRUE)

```

::::::

:::::: {.content-visible when-meta="params.education"}

## {{< iconify fa-solid:graduation-cap >}} Education

```{r}

read_sheet(google_page_id, sheet = "education") |> 
  mutate(
    x = str_glue("<strong>{university}</strong><br>{degree} in {major}"), 
    y = str_glue("{location}<br>{end}")
  ) |> 
  select(x, y) |> 
  kbl(
    escape = FALSE,
    col.names = NULL,
    align = c('l', 'r')
  ) |>
  kable_styling(full_width = TRUE)

```

::::::

:::::: {.content-visible when-meta="params.publications"}

## {{< iconify fa6-solid:book >}} Publications

#### *Peer-reviewed journal articles*

```{r}

bib |> 
  filter(collection == "Article") |> 
  format_entries(buttons = FALSE) |> 
  make_blocks()

```

<!-- #### *Manuscripts*

```{r}
#| eval: false

bib |> 
  filter(collection == "Manuscript") |> 
  format_entries(buttons = FALSE) |> 
  make_blocks()

``` 
-->

#### *Book reviews*

```{r}

bib |> 
  filter(collection == "Review") |> 
  format_entries(buttons = FALSE) |> 
  make_blocks()

```

#### *Technical reports*

```{r}

bib |> 
  filter(collection == "Report") |> 
  format_entries(buttons = FALSE) |> 
  make_blocks()

```

::::::

:::::: {.content-visible when-meta="params.funding"}

## {{< iconify fa-solid:hand-holding-usd >}} Grants, Fellowships, and Awards

```{r}

read_sheet(google_page_id, sheet = "funding") |> 
  filter(result == "Awarded") |> 
  mutate(collection = "Funding") |> 
  format_entries(buttons = FALSE) |> 
  make_blocks()

```
::::::

:::::: {.content-visible when-meta="params.presentations"}

## {{< iconify fa6-solid:desktop >}} Presentations

```{r}

bib |> 
  filter(collection == "Presentation") |> 
  format_entries(buttons = FALSE) |> 
  make_blocks()

```

::::::

:::::: {.content-visible when-meta="params.teaching"} 

## {{< iconify fa-solid:chalkboard-teacher >}} Teaching {#teaching}

:::::: blocks
::: {.cv-chunk style="margin-bottom:1em;"}
**Teaching interests**. Behavioral Ecology, Human Ecology, Human Prehistory,
Hunter-Gatherers, Conservation & Sustainability, Ethnoarchaeology, GIS/Spatial
Analysis, Quantitative Data Analysis, Archaeological Method & Theory, North
American Prehistory
:::

```{r}

read_sheet(google_page_id, sheet = "teaching") |> 
  group_by(university, department) |> 
  arrange(year, .by_group = TRUE) |> 
  summarize(
    courses = paste0(str_glue(
      
      "<li>{year} {semester} <strong>{position}</strong>. {course} </li>"
      
    ), collapse = "\n")
  ) |> 
  rowwise() |> 
  mutate(
    teaching = str_glue(
      
      "<p>{university}, Department of {department}</p><ul>{courses}</ul>"
      
    ),
  ) |> 
  ungroup() |> 
  pull(teaching) |> 
  HTML() |> 
  div(class = "cv-chunk")

```

::::::
::::::

:::::: {.content-visible when-meta="params.affiliations"}

## {{< iconify fa-solid:people-arrows >}} Professional Affiliations {#affiliations}

::: cv-chunk
```{r}

read_sheet(google_page_id, sheet = "affiliations") |> 
  mutate(
    end = ifelse(is.na(end), "present", end),
    x = str_glue("<a href='{url}'>{organization}</a>"), 
    y = str_glue("{start}-{end}")
  ) |> 
  select(x, y) |> 
  kbl(
    escape = FALSE,
    col.names = NULL,
    align = c('l', 'r')
  ) |>
  kable_styling(full_width = TRUE)

```
:::
::::::

:::::: {.content-visible when-meta="params.synergy"}

## {{< iconify fa-solid:hands-helping >}} Service, Outreach, and Other Activities

#### *University of Colorado, Boulder*

```{r}
#| eval: !expr params[["synergy"]]

read_sheet(google_page_id, sheet = "synergy") |> 
  filter(
    type == "university service", 
    university == "University of Colorado"
  ) |> 
  mutate(
    collection = "Synergy",
    status = ifelse(
      status == "active",
      paste0("<span style='color: #2B8A12; font-weight: bold;'>", status, "</span>"),
      paste0("<strong>", status, "</strong>")
    ),
    status = map(status, HTML)
  ) |> 
  format_entries(buttons = FALSE) |> 
  make_blocks()
  
```

#### *University of Utah*

```{r}
#| eval: !expr params[["synergy"]]

read_sheet(google_page_id, sheet = "synergy") |> 
  filter(
    type == "university service", 
    university == "University of Utah"
  ) |> 
  mutate(
    collection = "Synergy",
    status = ifelse(
      status == "active",
      paste0("<span style='color: #2B8A12; font-weight: bold;'>", status, "</span>"),
      paste0("<strong>", status, "</strong>")
    ),
    status = map(status, HTML)
  ) |> 
  format_entries(buttons = FALSE) |> 
  make_blocks()
  
```

#### *Outreach*

```{r}
#| eval: !expr params[["synergy"]]

read_sheet(google_page_id, sheet = "synergy") |> 
  filter(type == "outreach") |> 
  mutate(
    collection = "Synergy",
    status = ifelse(
      status == "active",
      paste0("<span style='color: #2B8A12; font-weight: bold;'>", status, "</span>"),
      paste0("<strong>", status, "</strong>")
    ),
    status = map(status, HTML)
  ) |> 
  format_entries(buttons = FALSE) |> 
  make_blocks()
  
```

::::::

:::::: {.content-visible when-meta="params.committees"}
::::::

:::::: {.content-visible when-meta="params.students"}
::::::

:::::: {.content-visible when-meta="params.development"}
::::::

:::::: {.content-visible when-meta="params.fieldwork"}
## {{< iconify fa6-solid:person-hiking >}} Fieldwork

*Multi-year projects are repeated with the number of weeks worked each year.*

```{r}
#| eval: !expr params[["fieldwork"]]

read_sheet(google_page_id, sheet = "fieldwork") |>
  arrange(desc(year)) |>
  mutate(collection = "Fieldwork") |> 
  format_entries(buttons = FALSE) |> 
  make_blocks()

```
::::::

## {{< iconify fa6-solid:envelope >}} References

*Available upon request.*

:::::::::
